---
title: "class04"
author: "Kandace Griffin"
date: "2/3/2022"
output: html_document
---

```{r setup, include=FALSE, cache = FALSE}
require("knitr") 
## setting working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

<!-- Runs the code but does not output to the document (include=FALSE) -->
```{r include=FALSE}
source(file="scripts/app04.R")
```

### Sea Lamprey water depth on spawning migration in the **White River, Michigan** 2021.

We had `r length(unique(positions$tag_id))` fish tracks through the White River. A subset of `r length(unique(press$tag_id))` fish were tagged with pressure tags to determine fish depth. Sea lamprey were a maximum `r max(press$fish_height_uncalibrated)` meters above the river bottom.

#### Sea lamprey height off bottom vs. water depth
```{r echo=FALSE}
plot(plot1)
```

#### Sea lamprey height off bottom by sex
```{r echo=FALSE}
plot(plot4)
```
***
Visit the [GLFC website](http://www.glfc.org/control.php) to find out more about efforts to control sea lamprey in the Great Lakes.
